---
title: "Lab 07 - Modelling course evaluations"
author: "Kiet Lam"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)
library(ggplot2)
```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
# add code here
score_viz <- evals %>% ggplot(aes(x = score)) +
          geom_histogram(binwidth = 0.2) + 
          geom_freqpoly(binwidth = 0.2)
score_viz

sum_score <- evals %>% summarise( 
    mean_score = mean(score, na.rm = TRUE),
    median_score = median(score, na.rm = TRUE)
  )

sum_score
```

The distribution of the histogram can be seen as left-skewed (negatively skewed). To support this, note that a left-skewed distribution will have the median value being greater than the mean value, given that the mean score (4.175 to 3dp) is less than the median score (4.3) it suffice to say that the distribution of scores is left-skewed.

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
bty_avg_vs_score_point <- evals %>% ggplot(aes(y = score, x = bty_avg)) +
                  geom_point()

bty_avg_vs_score <- evals %>% ggplot(aes(y = score, x = bty_avg)) +
                  geom_jitter()

bty_avg_vs_score_point
bty_avg_vs_score
```

Given that that bty_avg is an average, using only geom_point will make the variables of the data seem discrete but that is not the case. Geom_jitter adds some randomness in order to make data visualisation more appropriate.

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

score = 3.88 + 0.0666*bty_avg

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit,eval=FALSE}
bty_avg_vs_score2 <- evals %>% ggplot(aes(y = score, x = bty_avg)) +
                  geom_jitter() + geom_smooth(method = lm)
bty_avg_vs_score2
```

3. Interpret the slope of the linear model in context of the data.

For every increase in one unit of bty_avg, the score increases by 6.66% (to 3sf).

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

When the bty_avg = 0, the score is 3.88 (to 3sf) The intercept doesn't make sense in this context because there are no score values with 0 for a bty_avg.

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)$r.squared
```

Given that the value found for R^2 is close to 0, it is suffice to say that the explanatory variable/predictor (bty_avg) has very little correlation to the response variable (score), i.e. bty_avg seems to not play a big factor in the result of the score.

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(score_bty_aug, aes(x =.fitted, y = .resid)) + 
        geom_jitter() +
        geom_hline(aes(yintercept = 0),linetype = "dashed")

```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
# ... 
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

*Add your narrative here. Use in-line code!*

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

```{r eval = FALSE}
ggplot(___) + ...
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
